Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-08-13 Latex_files/Thesis/chapters/chapter 3/main.tex
updates to ch3

\subsection{Stationary beam}
Consider below in Fig.~\ref{fig:stationary_beam} the frames taken from a nucleation 
event in supersaturated glycine solution ($S=1.03$), the beam is a stationary being 
$\approx3.5 \mu m$ from the droplet edge. After a period of roughly 5 minutes a 
nucleus forms at the trap focus, growing quickly (growth rate was approximated using
imageJ to be on the order of $700\ \mu m^2/min$) from the focal point of the trap 
until after roughly $6$ seconds the crystal escapes. Comparing to previous literature
using optical tweezers shows that the growth rate is only loosely connected to the 
solutions supersaturation. Local conditions play a much larger role in the growth 
rate than just the concentration \cite{Flannigan2023}. A likely reason that the trap 
is escaped is due to the fact that crystal is far too large to be held in place and 
is in fact still growing as the solution is supersaturated. The key take away to 
remember is that the beam has no real influence over the crystal shape, instead 
it grows outward from the trap focus.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:stationary_beam}
\end{figure}

\subsection{Moving Beam}
\label{sec:stationary}
To test if a rapidly moving silica bead could generate the necessary shear rate 
for crystal nucleation we wanted to see if a trapped silica bead could be trapped
and moved in an aqueous solution. $20\ \mu L$ of glycine and water ($S=1.03$) was added to $10\ \mu L$ of a dilute water-silica mixture making the solution undersaturated ($S\approx0.7$). However, due to the beam's motion we instead 
encountered several unexpected results.

@@

\subsection{Direct trapping of Glycine clusters}
One common aspect involving these droplets is the fact when brought to the laser 
focus the droplets would nucleate immediately \cite{Liao2022}. We made up a 
solution similar to Sec~\ref{sec:stationary} but without any silica droplets, 
we once again focused the beam close to the droplet edge. Again after a few 
minutes of irradiation we noted the presence of droplets, because no silica had 
been added these droplets had to be from the glycine solution. Trapping these

@@

\section{Summary of Moving Beam Phenomena}
To summarise, the introduction of a moving beam helps to accelerate the local
growth of a newly formed crystal. This is due to the presence of glycine droplets
that accumulate near the interface between the liquid solution and air.

\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{galvano_diagram.pdf}
	\caption{Diagram outlining how a moving beam assists in the growth of a crystal
		nucleus. (a) a crystal nucleus is partially trapped by a moving beam with 
		solute droplets close to its surface. (b) droplets close to the laser
		focus are drawn in by gradient forces and moved towards the crystal surface.
		(c) these droplets provide material to the main crystal, resulting in
		localised growth around the laser focus. (d) eventually the crystal area 
		either fully surrounds the laser focus or the solution surrounding the laser
		is depleted of solute material.}
\end{figure}

>>>>

\subsection{Stationary beam}
\label{sec:stationary}
Consider below in Fig.~\ref{fig:stationary_beam} the frames taken from a nucleation 
event in supersaturated glycine solution ($S=1.03$), the beam is a stationary being 
$\approx3.5 \mu m$ from the droplet edge. After a period of roughly 5 minutes a 
nucleus forms at the trap focus, growing quickly (growth rate was approximated using
imageJ to be on the order of $700\ \mu m^2/min$) from the focal point of the trap 
until after roughly $6$ seconds the crystal escapes. Comparing to previous literature
using optical tweezers shows that the growth rate is only loosely connected to the 
solutions supersaturation. Local conditions play a much larger role in the growth 
rate than just the concentration \cite{Flannigan2023}. A likely reason that the trap 
is escaped is due to the fact that crystal is far too large to be held in place and 
is in fact still growing as the solution is supersaturated. The key take away to 
remember is that the beam has no real influence over the crystal shape, instead 
it grows outward from the trap focus.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.7\linewidth]{frames_no_beam_movement.pdf}
	\caption{Laser induced nucleation at the edge of a droplet of supersaturated 
	glycine solution. (b) shows the first instance of a crystal nucleus, growing 
	quickly through (c)-(e) until after $6.665\ s$ the crystal begins to escape the trap.}
	\label{fig:stationary_beam}
\end{figure}

\subsection{Moving Beam}
\label{sec:moving}
To test if a rapidly moving silica bead could generate the necessary shear rate 
for crystal nucleation we wanted to see if a trapped silica bead could be trapped
and moved in an aqueous solution. $20\ \mu L$ of glycine and water ($S=1.03$) was added to $10\ \mu L$ of a dilute water-silica mixture making the solution undersaturated ($S\approx0.7$). However, due to the beam's motion we instead 
encountered several unexpected results.

@@

\subsection{Direct trapping of Glycine clusters}
\label{sec:clusters}
One common aspect involving these droplets is the fact when brought to the laser 
focus the droplets would nucleate immediately \cite{Liao2022}. We made up a 
solution similar to Sec~\ref{sec:stationary} but without any silica droplets, 
we once again focused the beam close to the droplet edge. Again after a few 
minutes of irradiation we noted the presence of droplets, because no silica had 
been added these droplets had to be from the glycine solution. Trapping these

@@

\section{Summary of Moving Beam Phenomena}
To summarise, the introduction of a moving beam helps to accelerate the 
local growth of a newly formed crystal. This is due to the presence of 
glycine droplets that accumulate near the interface between the liquid 
solution and air. The theory behind the localised growth can be summarised 
thusly.

Initial nucleation is similar to typical optical trapping induced nucleation,
with the air solution interface limiting the molecular mobility of the solute
molecules \cite{Liao2022, Sugiyama2009, Gowayed2021}. The moving beam front 
can influence the motion of the nucleus initially, but eventually the drag 
force means the crystal is not moved by the optical trap. Localised crystal
growth occurs when the trap is close to or partially over the interface of 
the crystal (see figure~\ref{fig:local_nucleation}(a)). As shown in \ref{sec:clusters}, the optical trap can manipulate these droplets similar 
to microspheres. When in close proximity to the trap these droplets are 
brought towards the crystal surface (see figure~\ref{fig:local_nucleation}(b)). 
These provide material that grows the crystal around that region (see figure~\ref{fig:local_nucleation}(c)). Eventually the local solution is either 
depleted of solute material or the crystal front has grown to fully encompass 
the trap, preventing further growth (see figure~\ref{fig:local_nucleation}(d)). 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{galvano_diagram.pdf}
	\caption{Diagram outlining how a moving beam assists in the growth of a crystal
		nucleus. (a) a crystal nucleus is partially trapped by a moving beam with 
		solute droplets close to its surface. (b) droplets close to the laser
		focus are drawn in by gradient forces and moved towards the crystal surface.
		(c) these droplets provide material to the main crystal, resulting in
		localised growth around the laser focus. (d) eventually the crystal area 
		either fully surrounds the laser focus or the solution surrounding the laser
		is depleted of solute material.}
	\label{fig:local_nucleation}
\end{figure}

The reason the seed crystals saw no further crystal growth when irradiated 
with the trap is due to the fact that these experiments were carried out 
in a bulk solution, absent of any interfaces. As such the clusters seen in
\ref{sec:moving} \& \ref{sec:clusters} are not present and cannot provide
material to accelerate crystal growth.
